CFHTLens Weak Lensing Emulator and Cosmological Constraints from the Minkowski Functionals and Moments

### 2014-12-02 Paper_minkowski/paper.tex
update paper and figures

\subsection{Robustness}
%
The purpose of this paragraph is to convince the reader that the cosmological constraints we show in this paper are numerically robust, i.e. they are reasonably stable once we consider an increasing number of Principal Components. These stability plots are shown in Figure

@@

\begin{table*}
\begin{tabular}{c|c|c|c|c||c}
Parameters & Descriptors & $\theta_G$ & Additional details & Short description & Relevant Figures/Tables \\ \hline \hline
$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask & $1\sigma$ contours from CFHTLens data & Figure \ref{contours3comp} \\ \hline 
$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask &\pbox{20cm}{$1\sigma$ contours from simulations \\ for robustness test}  & Figure \ref{contours3comp} \\
\end{tabular}
\caption{Summary table of our results}
\label{summarytable}
\end{table*}

>>>>

\subsection{Robustness}
%
The purpose of this paragraph is to convince the reader that the cosmological constraints we show in this paper are numerically robust, i.e. they are reasonably stable once we consider an increasing number of Principal Components. These stability plots are shown in Figure \ref{robustnessfig}

\begin{figure*}
\includegraphics[scale=0.4]{Figures/robustness_pca.eps}
\caption{Stability plot}
\label{robustnessfig}
\end{figure*}

@@

\begin{table*}
\begin{tabular}{c|c|c|c|c||c}
Parameters & Descriptors & $\theta_G$ & Additional details & Short description & Relevant Figures/Tables \\ \hline \hline
$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask & $1\sigma$ contours from CFHTLens data & Figure \ref{contours3comp} \\ \hline 
$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask &\pbox{20cm}{$1\sigma$ contours from simulations \\ for robustness test}  & Figure \ref{robustnessfig} \\
\end{tabular}
\caption{Summary table of our results}
\label{summarytable}
\end{table*}
